A Bayesian ranking statistic to find high-mass black holes in LIGO--Virgo data

### 2021-04-08 main.tex
Updates from Overleaf

\begin{figure}[!ht]
{\centering \includegraphics[width=0.85\linewidth]{images/bcr_cdf_smaller_legend.png} }
\caption[BCR distribution example]{Histograms represent the survival function (1-CDF) from our high-mass selection of background triggers (grey) and simulated signals (blue) triggers obtained from \pycbc's search of data from $\text{August 13 - 21, 2017}$. Vertical lines mark the $\text{ln}\ \bcr$ of IAS's GW170817A and GWTC-1's GW170814.}\label{fig:bcrCdf}
\end{figure}

@@

\begin{figure}[!ht]
{\centering \includegraphics[width=0.85\linewidth]{images/bcr_cdf_smaller_legend.png} }
\caption[BCR distribution example]{This plot is analogous to Fig.~\ref{fig:bcrCdf}, but without using the post-processing step to marginalize over PSD statistical uncertainties. Without the post-processing step, there is a greater overlap between the background (grey) and foreground (blue) survival functions. For more details about this plot, refer to the caption of Fig.~\ref{fig:bcrCdf}.}\label{fig:bcrCdfUnmarginalized}
\end{figure}

>>>>

\begin{figure}[!ht]
{\centering \includegraphics[width=0.85\linewidth]{images/reweighted_bcr_cdf_smaller_legend.png} }
\caption[BCR distribution example]{Histograms represent the survival function (1-CDF) from our high-mass selection of background triggers (grey) and simulated signals (blue) triggers obtained from \pycbc's search of data from $\text{August 13 - 21, 2017}$. Vertical lines mark the $\text{ln}\ \bcr$ of IAS's GW170817A and GWTC-1's GW170814.}\label{fig:bcrCdf}
\end{figure}

@@

\begin{figure}[!ht]
{\centering \includegraphics[width=0.85\linewidth]{images/orig_bcr_cdf_smaller_legend.png} }
\caption[BCR distribution example]{This plot is analogous to Fig.~\ref{fig:bcrCdf}, but without using the post-processing step to marginalize over PSD statistical uncertainties. Without the post-processing step, there is a greater overlap between the background (grey) and foreground (blue) survival functions. For more details about this plot, refer to the caption of Fig.~\ref{fig:bcrCdf}.}\label{fig:bcrCdfUnmarginalized}
\end{figure}
